### 2012-12-05 MSteenhagen-CV.tex
Modified AoC.
Blocked out some info.
Added some info to .tex head
Removed foreign entries.
Added Warwick talk
Added Mindgrad

%%% A template to produce a nice-looking Curriculum Vitae.
%%% Kieran Healy <kjhealy@gmail.com>
%%% Most recent version is at http://kjhealy.github.com/kjh-vita
%%%
%%% ------------------------------------------------------------------------
%%% Requirements (should be included in a modern tex distribution):
%%% ------------------------------------------------------------------------
%%% xelatex
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%%
%%% ------------------------------------------------------------------------
%%% Optional
%%% ------------------------------------------------------------------------
%%% git
%%% vc.sty
%%% revnum.sty
%%% Fonts
%%%
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip, 
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or 
%%% remove these as needed.
%%%------------------------------------------------------------------------

@@

\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ Century Philosophy; Political Philosophy.

@@

% \newpage

%% Presentations
\marginhead{{\vskip 0.4em}Talks}
\medskip

@@

\ind 2012. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} PhD Studentship Award. (£36.000)

@@

\rfoot{\footnotesize{\today}}
% %% Publications

%  
% \normalsize
% 
% \bigskip
% \noindent\emph{Journal articles \vspace{0.05in}}
%  
% %% Use revnumerate environment if numbered publications are needed. 
% %% (Include it above in the preamble).
% %% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
% %% \begin{revnumerate}
% 
% \ind Marion Fourcade and Kieran Healy. 2007. ``\href{http://arjournals.annualreviews.org/doi/pdf/10.1146/annurev.soc.33.040406.131642}{Moral Views of Market Society}.'' \emph{Annual Review of Sociology} 33:~285--311. 
% 
% \ind Kieran Healy. 2006. ``\href{http://www.kieranhealy.org/files/papers/presumed-consent.pdf}{Do Presumed Consent Laws Raise Organ Procurement Rates?}'' \emph{DePaul Law Review} 55:~1017--1043. 
% 
% \ind Kieran Healy. 2004. ``\href{http://www.kieranhealy.org/files/papers/asr2004.pdf}{Altruism as an Organizational Problem: The Case of Organ Procurement}.''
%  \emph{American Sociological Review} 69:~387--404.
% 
% \ind Kieran Healy. 2002. ``\href{http://www.kieranhealy.org/files/papers/jpp.pdf}{Digital Technology and Cultural Goods}.'' \emph{Journal of
%   Political Philosophy} 10:~478--500. 
% 
% \ind Kieran Healy. 2002. ``\href{http://www.kieranhealy.org/files/papers/culture-newecon.pdf}{What's New for Culture in the New Economy?}'' \emph{Journal
%   of Arts Management, Law and Society} 32:~86--103. 
% 
% 
% \ind Kieran Healy. 2000. ``\href{http://www.kieranhealy.org/files/papers/embed-alt.pdf}{Embedded Altruism: Blood Collection Regimes and the European
%   Union's Donor Population}.'' \emph{American Journal of Sociology} 105:~1633--\,1657.
% 
% 
% \ind Kieran Healy. 1999.  ``\href{http://www.kieranhealy.org/files/papers/ts.pdf}{The Emergence of \textsc{hiv} in the U.S. Blood Supply: Organizations,
%   Obligations and the Management of Uncertainty}.'' \emph{Theory and Society} 28:~529--558.
% 
% 
% \ind Bruce Western and Kieran Healy. 1999. ``\href{http://www.kieranhealy.org/files/papers/western-healy99.pdf}{Explaining the OECD Wage Slowdown:
% Recession or Labor Decline?}''  \emph{European Sociological Review}
% 15:~233--249.
% 
% 
% \ind  Kieran Healy. 1998.  ``\href{http://www.kieranhealy.org/files/papers/constraint98.pdf}{Conceptualising Constraint: Mouzelis, Archer and the concept of
%   social structure}.'' \emph{Sociology} 32:~509--522. 
% 
% %\end{revnumerate}
% %\newpage
% \bigskip
% 
% \noindent\emph{Book chapters \vspace{0.05in}}
% % \renewcommand{\labelenumi}{\textsc{c}\theenumi.}
% % \begin{revnumerate}
% 
% \ind Kieran Healy. Forthcoming. ``Social Structure, Gifts and Norms in \emph{The Story of Qiu Ju},'' in \emph{Norms and Values: The Role of Social Norms as Instruments of Value Realisation}, edited by Michael Baurmann, Geoffrey Brennan, Robert E. Goodin and Nicholas Southwood. Baden Baden: Nomos Verlag.
% 
% \ind Kieran Healy. 2008. ``Lo Scambio di Doni,'' in \emph{L'Altro in Me: Dono del Sangue fra Culture, Pratiche e Identità}, edited by Annamaria Fantauzzi. Milano: \textsc{avis} Nazionale, 36--42. 
% 
% \ind Kieran Healy. 2007. ``Sociology,'' in \emph{A Companion to Contemporary Political Philosophy} (Second Edition), edited by Robert E. Goodin, Philip Pettit and Thomas Pogge. New York: Blackwell, 90--122. 
% 
% \ind  Kieran Healy. 2004. ``Sacred Markets and Secular Ritual in the Organ Transplant
% Industry,'' in \emph{The Sociology of the Economy}, edited by Frank Dobbin. New
% York: Russell Sage, 336--359.
% 
% \ind Bruce Western and Kieran Healy.  2001.  ``Wage Growth and Labor Decline in the
% Industrialized Democracies, 1965--1993,'' in \emph{Unemployment in the New
%   Europe}, edited by Nancy Bermeo. New York: Cambridge University Press,
% 121--144.
% 
%  \ind  Kieran Healy. 1998. ``The New Institutionalism and Irish Social Policy,'' in
% \emph{Social Policy in Ireland: Principles, Practice and Problems}, edited by
% Se\'{a}n Healy and Brigid Reynolds. Dublin: Oak Tree Press, 59--83.
% 
% %\end{revnumerate}
% 
% \bigskip 
%  
% %\newpage
% \noindent\emph{Reviews and other occasional writing \vspace{0.05in}}
% 
% %\renewcommand{\labelenumi}{\textsc{r}\theenumi.}
% %\begin{revnumerate}
% \ind Kieran Healy. 2009. \href{http://www.journals.uchicago.edu/doi/pdf/10.1086/605757}{Review} of \emph{Pop Finance} by Brooke Harrington. \emph{American Journal of Sociology} 115:~309--12.
% 
% \ind Kieran Healy. 2007. ``\href{http://www.kieranhealy.org/files/reviews/socforum-article.pdf}{A Wealth of Notions}.'' Review
% Essay on \emph{Freakonomics} by Steven Levitt and Stephen Dubner. \emph{Sociological Forum} 22:~119--125. 
% 
% \ind  Kieran Healy. 2006. ``Sacred.'' In \emph{International Encyclopedia of Economic Sociology}, edited by Jens Beckert and Milan Zafirovski. London: Routledge, 588--589. 
% 
% \ind  Kieran Healy. 2005. \href{http://www.kieranhealy.org/files/reviews/klinenberg.pdf}{Review} of \emph{Heat Wave} by Eric Klinenberg. \emph{Imprints} 8:~283--289.
% 
% \ind  Kieran Healy. 2005. \href{http://www.kieranhealy.org/files/reviews/fox.pdf}{Review} of \emph{An R and S-PLUS Companion to Applied Regression}, by John Fox. \emph{Sociological Methods and Research} 34:~137--140.
% 
% \ind  Kieran Healy. 2005. ``\href{http://www.kieranhealy.org/files/reviews/henwood.pdf}{After the Ball was Over}.'' Review of \emph{After the New
%   Economy} by Doug Henwood. \emph{European Economic Sociology Newsletter} 6 (3):~37--38.
% 
% \ind  Kieran Healy. 2004. ``The Abundance of the Heart.'' Review of \emph{A Man After His Own Heart} by Charles
% Siebert. \emph{Australian Review of Public Affairs}, October. Reprinted in the
% \emph{Australian Financial Review}, October 22nd.
% 
% \ind  Kieran Healy. 2003. \href{http://links.jstor.org/sici?sici=0094-3061%28200303%2932%3A2%3C252%3AAEATOC%3E2.0.CO%3B2-F}{Review} of \emph{Against Essentialism} by Stephan Fuchs.
% \emph{Contemporary Sociology} 32:~252--254.
% 
% \ind  Kieran Healy. 2001. Review of \emph{Market Society} by Don Slater and Fran Tonkiss. \emph{European
%       Economic Sociology Newsletter} 3 (1):~31--32.
% 
% 
% \ind  Kieran Healy. 1999. \href{http://links.jstor.org/sici?sici=0094-3061%28199903%2928%3A2%3C210%3ACPRCAS%3E2.0.CO%3B2-C}{Review} of \emph{Comparative Politics} by Mark Irving Lichbach and Alan S.
% Zuckerman. \emph{Contemporary Sociology} 28:~210--211.
% 
% 
% \ind  Kieran Healy. 1998. \href{http://www.kieranhealy.org/files/reviews/rule.pdf}{Review} of \emph{Theory and Progress in Social Science} by James Rule.  \emph{Theory
%   and Society}, 27:~435--441.
% 
% % %\end{revnumerate}
%  \bigskip

>>>>

%%% A template to produce a nice-looking Curriculum Vitae.
%%% Orginally produced by Kieran Healy <kjhealy@gmail.com>
%%% This version is adapted (only minimally) by Maarten Steenhagen.
%%% 
%%% ------------------------------------------------------------------------
%%% Requirements (should be included in a modern tex distribution):
%%% ------------------------------------------------------------------------
%%% xelatex
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%%
%%% ------------------------------------------------------------------------
%%% Optional
%%% ------------------------------------------------------------------------
%%% git
%%% vc.sty
%%% revnum.sty
%%% Fonts
%%%
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip, 
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or 
%%% remove these as needed.
%%%------------------------------------------------------------------------

@@

\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ C. Philosophy; Political Philosophy.

@@

\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Talks}
\medskip

\ind 2012. ``Two problems of co-consciousness.'' Department of Philosophy, University of Warwick, \href{http://www2.warwick.ac.uk/fac/soc/philosophy/news/conferences/mindgrad-2012/}{MindGrad 2012}. Respondent: Dr. Christoph Hoerl (Warwick).

\ind 2012. ``Imaginary Experience.'' University of Warwick, London-Warwick Graduate Mind Forum.

@@

\ind 2012. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} PhD Studentship Award. %(£36.000)

@@

\rfoot{\footnotesize{\today}}
